---
title: "MA615_Midterm"
author: "Bingtian Ye"
date: "2023-10-27"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("tidyverse","UpSetR","naniar","sf","stringr","scales","gridExtra")
```

```{css, echo=FALSE}
h1 {
    font-size: 1.5em; 
}
h2 {
    font-size: 1.3em;
}
h3 {
    font-size: 1.15em;
    padding-left: 20px;
}
```

## 1.read data

v1 (OpenFEMA Dataset: FEMA Web Disaster Summaries - v1, link = <https://www.fema.gov/openfema-data-page/fema-web-disaster-summaries-v1>) and v2 (OpenFEMA Dataset: Disaster Declarations Summaries - v2, link = <https://www.fema.gov/openfema-data-page/disaster-declarations-summaries-v2>). I observed some data provided by FEMA, and some of the data has nothing to do with flooding. For example, the content in WebDisasterDeclarations that is related to flooding is included in v2. So only the above two data are used.

```{r}
v1=read.csv("v1.csv",header=T)
v2=read.csv("v2.csv",header=T)
```

## 1.Data Fields

### v1 FEMA Web Disaster Summaries

```{=html}
<style>
table {
    width: 100%;
    font-size: 80%;
}
th {
    font-weight: bold;
    text-align: center;
}
td {
    text-align: center;
}
</style>
```
|            Name            |                            Description                             |
|:------------------------:|:--------------------------------------------:|
|       disasterNumber       | Unique identifier for each disaster. Can be used to merge datasets |
|   totalNumberIaApproved    |          Approved applications for Individual Assistance           |
|   totalAmountIhpApproved   |       Dollars approved for Individual and Households Program       |
|   totalAmountHaApproved    |              Dollars approved for Housing Assistance               |
|   totalAmountOnaApproved   |            Dollars approved for Other Needs Assistance             |
|   totalObligatedAmountPa   |           Dollars available for Public Assistance grants           |
| totalObligatedAmountCatAb  |  Dollars for Emergency Work Public Assistance (Categories A & B)   |
| totalObligatedAmountCatC2g |  Dollars for Permanent Work Public Assistance (Categories C to G)  |
|         paLoadDate         |              Date Public Assistance data was updated               |
|         iaLoadDate         |            Date Individual Assistance data was updated             |
|  totalObligatedAmountHmgp  |     Dollars obligated for the Hazard Mitigation Grant Program      |
|            hash            |                MD5 hash for the record's integrity                 |
|        lastRefresh         |                 Date the record was last refreshed                 |
|             id             |                      Unique ID for the record                      |

### v2 Disaster Declarations Summaries

```{=html}
<style>
table {
    width: 100%;
    font-size: 80%;
}
th {
    font-weight: bold;
    text-align: center;
}
td {
    text-align: center;
}
</style>
```
|           Name           |                                  Description                                   |
|:--------------------:|:------------------------------------------------:|
|  femaDeclarationString   |   Agency standard method for uniquely identifying Stafford Act declarations.   |
|      disasterNumber      |       The number of the disaster, unique. Can be used to merge datasets        |
|          state           |      The name or phrase describing the U.S. state, district, or territory      |
|     declarationType      |         Two character code that defines the disaster declaration type.         |
|     declarationDate      |                         Date the disaster was declared                         |
|        fyDeclared        |                 Fiscal year in which the disaster was declared                 |
|       incidentType       |                    Type of incident such as fire or flood.                     |
|     declarationTitle     |                             Title for the disaster                             |
|    ihProgramDeclared     | Whether the Individuals and Households program was declared for this disaster. |
|    iaProgramDeclared     |   Whether the Individual Assistance program was declared for this disaster.    |
|    paProgramDeclared     |     Whether the Public Assistance program was declared for this disaster.      |
|    hmProgramDeclared     |     Whether the Hazard Mitigation program was declared for this disaster.      |
|    incidentBeginDate     |                         Date the incident itself began                         |
|     incidentEndDate      |                         Date the incident itself ended                         |
|   disasterCloseoutDate   |         Date all financial transactions for all programs are completed         |
|      tribalRequest       |        Whether a declaration request was submitted by a Tribal Nation.         |
|      fipsStateCode       |              FIPS code used to identify US states and territories              |
|      fipsCountyCode      |             FIPS code used to identify US counties and equivalents             |
|        placeCode         |               FEMA's internal code system to recognize locations               |
|      designatedArea      |                  Geographic area included in the declaration                   |
| declarationRequestNumber |                   Number assigned to the declaration request                   |
|     lastIAFilingDate     |                    Last date when IA requests can be filed.                    |
|       lastRefresh        |             Date the record was last updated in the API data store             |
|           hash           |                MD5 Hash of the fields and values of the record                 |
|            id            |                        Unique ID assigned to the record                        |

## Data preparing

By observing the contents of the data table, I decided to use v2 as the main database, and then merged the two databases based on the disasterNumber field. \### Data preparing for v2 First select the required columns. Based on observation, the selected columns are as follows: disasterNumber, state, declarationType, declarationDate, incidentType, declarationTitle, ihProgramDeclared, iaProgramDeclared, paProgramDeclared, hmProgramDeclared, fipsStateCode, fipsCountyCode, id

```{r}
v2 <- v2 |>
  select(disasterNumber, state, declarationType, declarationDate, incidentType, declarationTitle, ihProgramDeclared, iaProgramDeclared, paProgramDeclared, hmProgramDeclared, fipsStateCode, fipsCountyCode, id)
```

Split column declarationDate and select the years in 2020 and 2021

```{r}
v2 <- v2 |>
  mutate(year = substr(declarationDate, 1, 4),
         month = substr(declarationDate, 6, 7),
         day = substr(declarationDate, 9, 10)) |>
  filter(year == "2020" | year == "2021") |>
  select(!declarationDate)
```

Filter the rows where incidentType is flood, and replace the abbreviation of declarationType with the completion name (DR = Major Disaster Declaration, EM = Emergency Declaration, FM = Fire Management Assistance Declaration).

```{r}
v2 <- v2 |>
  filter(incidentType == "Flood") |>
  mutate(declarationType = case_when(
    declarationType == "DR" ~ "Major Disaster Declaration",
    declarationType == "EM" ~ "Emergency Declaration",
    declarationType == "FM" ~ "Fire Management Assistance Declaration"
  ))
```

Remove columns whose values are the same

```{r}
v2 <- v2 |>
  select_if(~ n_distinct(.) > 1)
```

### Data preparing for v1 and Merge two dataset

Remove the following columns: paLoadDate, iaLoadDate, hash, lastRefresh, id. And then merge to dataset by using key "diasasterNumber".

```{r}
v1 <- v1 |>
  select(-paLoadDate, -iaLoadDate, -hash, -lastRefresh, -id)
new_data <- v2 |>
  left_join(v1, by = "disasterNumber")
colnames(new_data)
# check the NA value (missing data)
gg_miss_upset(new_data)
```

When the values of the four columns totalNumberIaApproved, totalAmountIhpApproved, totalAmountHaApproved, and totalAmountOnaApproved are NA, we observe that the value of ihProgramDeclared is 0, so we believe that they have not received donations from the Individuals and Households program. Therefore, the missing values in these four columns are set to 0.

```{r}
#Verify whether the guess is correct
rows_with_na <- new_data |>
  filter(
    is.na(totalNumberIaApproved) |
    is.na(totalAmountIhpApproved) |
    is.na(totalAmountHaApproved) |
    is.na(totalAmountOnaApproved)
  )

# If the result is TRUE, the guess is correct, otherwise, the guess is incorrect.
all(rows_with_na$ihProgramDeclared == 0)

#Since the value of above is TRUE, so we set four columns' NA value to 0.
new_data <- new_data |>
  mutate(
    totalNumberIaApproved = ifelse(is.na(totalNumberIaApproved), 0, totalNumberIaApproved),
    totalAmountIhpApproved = ifelse(is.na(totalAmountIhpApproved), 0, totalAmountIhpApproved),
    totalAmountHaApproved = ifelse(is.na(totalAmountHaApproved), 0, totalAmountHaApproved),
    totalAmountOnaApproved = ifelse(is.na(totalAmountOnaApproved), 0, totalAmountOnaApproved)
  )

# Since disaster 4571 is the only disaster that totalObligatedAmountPa, totalObligatedAmountCatAb, totalObligatedAmountCatC2g. I think it haven't got the money from the three parts, so set it's value to 0.
new_data <- new_data |>
  mutate(
    totalObligatedAmountPa = ifelse(is.na(totalObligatedAmountPa), 0, totalObligatedAmountPa),
    totalObligatedAmountCatAb = ifelse(is.na(totalObligatedAmountCatAb), 0, totalObligatedAmountCatAb),
    totalObligatedAmountCatC2g = ifelse(is.na(totalObligatedAmountCatC2g), 0, totalObligatedAmountCatC2g)
  )

#check the NA value again, if the value is FALSE, the dataset haven's any NA value.
any(is.na(new_data))

#The value is NA, which means the dataset haven't NA value. We can continue to the follow steps.
```

## EDA

### Disaster by States

```{r,message=F}
us_states <- st_read("https://eric.clst.org/assets/wiki/uploads/Stuff/gz_2010_us_040_00_5m.json")

# Read the disaster data
disaster_data <- new_data

# Process the disaster data
# Dropping duplicates to ensure we count each disaster only once per state
state_disaster_counts <- disaster_data |>
  distinct(disasterNumber, fipsStateCode, .keep_all = TRUE) |>
  count(fipsStateCode) |>
  mutate(fipsStateCode = as.character(fipsStateCode)) |>
  rename(StateFIPS = fipsStateCode, Disasters = n)

# Make sure the FIPS codes have leading zeros
state_disaster_counts$StateFIPS <- str_pad(state_disaster_counts$StateFIPS, width = 2, side = "left", pad = "0")

# Join the disaster data with the state geometries
merged_data <- left_join(us_states, state_disaster_counts, by = c("STATE" = "StateFIPS"))

# Plot the map
plot1 <- ggplot(data = merged_data) +
  geom_sf(aes(fill = Disasters)) +
  scale_fill_gradient(low = "lightblue", high = "darkred", na.value = "white") +
  theme_minimal() +
  labs(title = "Number of Disasters by State", fill = "Disasters") +
  coord_sf(xlim = c(-170, -65), ylim = c(25, 72))

# Display the plot
print(plot1)
```

According to the results, there will be fewer flood disasters in the United States in 2020 and 2021, and the distribution will be more scattered.

### Count of Counties by Program Declaration and Value

```{r,message=F}
declared_data <- new_data |>
  group_by(fipsStateCode, fipsCountyCode) |>
  summarise(
    ihProgramDeclared = sum(ihProgramDeclared, na.rm = TRUE),
    paProgramDeclared = sum(paProgramDeclared, na.rm = TRUE),
    hmProgramDeclared = sum(hmProgramDeclared, na.rm = TRUE),
    .groups = "drop"  
  )|>
  mutate(
    fipsStateCode = str_pad(fipsStateCode, width = 2, pad = "0"),
    fipsCountyCode = str_pad(fipsCountyCode, width = 3, pad = "0"),
    FipsCode = paste0(fipsStateCode, fipsCountyCode)  
  )|>
  select(
    -fipsStateCode,
    -fipsCountyCode
  )
# fipscode.csv is from https://transition.fcc.gov/oet/info/maps/census/fips/fips.txt and has been process by using excel
fips_codes <- read_csv("fipscode.csv", col_names = TRUE)

fips_codes <- fips_codes |>
  mutate(`FIPS code` = as.character(`FIPS code`))

declared_data_with_names <- declared_data |>
  left_join(fips_codes, by = c("FipsCode" = "FIPS code"))|>
  distinct(name, .keep_all = TRUE)
count_ihProgramDeclared <- declared_data_with_names |>
  count(ihProgramDeclared, name = "Count") |>
  mutate(Program = 'IH Program')

count_paProgramDeclared <- declared_data_with_names |>
  count(paProgramDeclared, name = "Count") |>
  mutate(Program = 'PA Program')

count_hmProgramDeclared <- declared_data_with_names |>
  count(hmProgramDeclared, name = "Count") |>
  mutate(Program = 'HM Program')

program_counts <- bind_rows(count_ihProgramDeclared, count_paProgramDeclared, count_hmProgramDeclared)|>
  pivot_longer(
    cols = c(ihProgramDeclared, paProgramDeclared, hmProgramDeclared),
    names_to = "ProgramDeclaredType",
    values_to = "Value"
  )|>
  filter(!is.na(Value))

ggplot(program_counts, aes(x = ProgramDeclaredType, y = Count, fill = as.factor(Value))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "Count of Counties by Program Declaration and Value",
       x = "Program Declared Type",
       y = "Number of Counties",
       fill = "Value") +
  theme_minimal() +
  scale_fill_manual(values = c("lightyellow", "lightblue", "lightgreen"))

```

It can be seen that a county generally receives less than or equal to one aid plan from the same source. And the number of assistance programs from the Individuals and Households program and Public Assistance program is greater than that from the Individual Assistance program

### The total amount approved from different program

```{r}
Approved_data <- new_data |>
  distinct(disasterNumber,.keep_all = TRUE) |>
  mutate(as.factor(disasterNumber))|>
  filter(totalNumberIaApproved != 0, totalAmountIhpApproved != 0, totalAmountHaApproved != 0)|>
  select(disasterNumber, totalNumberIaApproved, totalAmountIhpApproved, totalAmountHaApproved) |>
  pivot_longer(
    cols = -disasterNumber,
    names_to = "FinancialType",
    values_to = "Amount"
  )|>
  group_by(disasterNumber) |>
  mutate(Proportion = Amount / sum(Amount),
         LabelPosition = cumsum(Amount) - (0.5 * Amount)) |>
  ungroup()

ggplot(Approved_data, aes(x = as.factor(disasterNumber), y = Amount, fill = FinancialType)) +
  geom_col() +
  scale_fill_manual(values = c("lightblue", "lightgreen", "lightyellow")) +
  geom_text(
    aes(label = scales::percent(Proportion, accuracy = 1), y = LabelPosition),
    color = "black",
    size = 3,
    vjust = 0.5,  
    check_overlap = TRUE
  ) +
  theme_minimal() +
  labs(x = "Disaster Number", y = "Total Amount", fill = "Financial Type")
```

The total amount approved for Housing Assistance is similar to The total amount approved for the Individual and Households Program, and basically no The number of disaster assistance applications that were approved for Individual Assistance. 

### The Public Assistance grant funding available in different disaster.

```{r}
AmongPA <- new_data |>
  distinct(disasterNumber,.keep_all = TRUE) |>
  select(disasterNumber,totalObligatedAmountPa)|>
  mutate(as.factor(disasterNumber))

ggplot(AmongPA) +
  aes(
    x = `as.factor(disasterNumber)`,
    y = totalObligatedAmountPa
  ) +
  geom_col(fill = "#4682B4") +
  labs(x = "Disaster Number", y = "Public Assistance grant funding", title = "The Public Assistance grant funding available in different disaster") +
  theme_minimal()
```

### The different types of public assistance grant funds available to recipients in U.S. dollars

```{r}
Funding <- new_data |>
  distinct(disasterNumber, .keep_all = TRUE) |>
  mutate(disasterNumber = as.factor(disasterNumber)) |>
  select(disasterNumber, totalObligatedAmountCatAb, totalObligatedAmountCatC2g) |>
  pivot_longer(
    cols = starts_with("totalObligatedAmount"),
    names_to = "Category",
    values_to = "Amount"
  )|>
  mutate(Category = recode(Category, 
                            "totalObligatedAmountCatAb" = "A and B",
                            "totalObligatedAmountCatC2g" = "C to G"))
Funding_long <- Funding |>
  group_by(disasterNumber) |>
  mutate(TotalAmount = sum(Amount)) |>
  ungroup()

ggplot(Funding_long, aes(x = as.factor(disasterNumber), y = Amount, fill = Category)) +
  geom_col() +
  scale_fill_manual(values = c("#FF7F50", "#E1FFFF"),
                    labels = c("A and B", "C to G")) +  
  geom_text(
    aes(label = scales::percent(Amount / TotalAmount, accuracy = 1)),
    position = position_stack(vjust = 0.5),
    size = 3,
    color = "black"
  ) +
  theme_minimal() +
  labs(x = "Disaster Number", y = "Public Assistance grant funding", fill = "Category",title="The different types of public assistance grant funds available to recipients in U.S. dollars") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  

```

It can be seen that most public assistance grant funds available are of type c to g.

## Combine Flood Information With Census

### read data and combine data

```{r,message=F}
# read data
houseunit2020 <- read_csv("houseunit2020.csv")
houseunit2021 <- read_csv("houseunit2021.csv")
population2020 <- read_csv("population2020.csv")
population2021 <- read_csv("population2021.csv")
poverty2020 <- read_csv("poverty2020.csv")
poverty2021 <- read_csv("poverty2021.csv")

# combine three datasets with same year, get Fipscode
data_2020 <- population2020 |>
  left_join(houseunit2020, by = "Geography") |>
  left_join(poverty2020, by = "Geography") |>
  mutate(Fipscode = substr(Geography, nchar(Geography)-4, nchar(Geography))) |>
  select(Fipscode, everything()) |>
  select(-Geography)

data_2021 <- population2021 |>
  left_join(houseunit2021, by = "Geography") |>
  left_join(poverty2021, by = "Geography") |>
  mutate(Fipscode = substr(Geography, nchar(Geography)-4, nchar(Geography))) |>
  select(Fipscode, everything()) |>
  select(-Geography)

# combine datasets with flood information dataset. If year is 2020, combine data_2020, otherwise, combine data_2021. 
flood_data <- new_data |>
  mutate(
    fipsStateCode = str_pad(fipsStateCode, width = 2, pad = "0"),
    fipsCountyCode = str_pad(fipsCountyCode, width = 3, pad = "0"),
    Fipscode = paste0(fipsStateCode, fipsCountyCode)  
  ) |>
  select(Fipscode, everything())
# Split the flood_data into two data frames
flood_data_2020 <- filter(flood_data, year == 2020)
flood_data_2021 <- filter(flood_data, year == 2021)
# Join with data_2020 and data_2021
flood_data_2020 <- flood_data_2020 |>
  left_join(data_2020, by = "Fipscode")
flood_data_2021 <- flood_data_2021 |>
  left_join(data_2021, by = "Fipscode")

# Combine the two data frames
final_data <- bind_rows(flood_data_2020, flood_data_2021)
```

### Group by state and disasterNumber

```{r,message=F}
data_withflood <- final_data|>
  group_by(disasterNumber, state) %>%
  summarise(
    Total_population = sum(`Total population`, na.rm = TRUE),
    HOUSE_UNIT = sum(`HOUSE UNIT`, na.rm = TRUE),
    Population_poverty_status_determined = sum(`Population for whom poverty status is determined`, na.rm = TRUE),
    totalNumberIaApproved = first(totalNumberIaApproved),
    totalAmountIhpApproved = first(totalAmountIhpApproved),
    totalAmountHaApproved = first(totalAmountHaApproved),
    totalAmountOnaApproved = first(totalAmountOnaApproved),
    totalObligatedAmountPa = first(totalObligatedAmountPa),
    totalObligatedAmountCatAb = first(totalObligatedAmountCatAb),
    totalObligatedAmountCatC2g = first(totalObligatedAmountCatC2g),
    totalObligatedAmountHmgp = first(totalObligatedAmountHmgp),
    Sum_Total_population = sum(`Total population`, na.rm = TRUE),
    Sum_HOUSE_UNIT = sum(`HOUSE UNIT`, na.rm = TRUE),
    Sum_Population_poverty_status_determined = sum(`Population for whom poverty status is determined`, na.rm = TRUE)
  ) 
```

## EDA after add datasets

### state population with Total Amount Approved

```{r}
amount_data <- data_withflood |>
  filter(!(totalNumberIaApproved == 0 & 
           totalAmountIhpApproved == 0 & 
           totalAmountHaApproved == 0 & 
           totalAmountOnaApproved == 0))

ggplot(amount_data, aes(x = Sum_Total_population)) +
  geom_area(aes(y = totalNumberIaApproved, fill = 'totalNumberIaApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountIhpApproved, fill = 'totalAmountIhpApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountHaApproved, fill = 'totalAmountHaApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountOnaApproved, fill = 'totalAmountOnaApproved'), alpha = 0.5) +
  scale_fill_manual(values = c('totalNumberIaApproved' = '#1f77b4',  
                               'totalAmountIhpApproved' = '#2ca02c', 
                               'totalAmountHaApproved' = '#ff7f0e',  
                               'totalAmountOnaApproved' = '#d62728'), 
                    labels = c('totalNumberIaApproved' = 'Total Number IA Approved',
                               'totalAmountIhpApproved' = 'Total Amount IHP Approved',
                               'totalAmountHaApproved' = 'Total Amount HA Approved',
                               'totalAmountOnaApproved' = 'Total Amount ONA Approved')) +
  labs(x = "Total Population", y = "Total Amount Approved", fill = "Metric" ,title = "state population with Total Amount Approved") +
  theme_classic()
```

### state HOUSE UNIT with Total Amount Approved

```{r}
ggplot(amount_data, aes(x = Sum_HOUSE_UNIT)) +
  geom_area(aes(y = totalNumberIaApproved, fill = 'totalNumberIaApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountIhpApproved, fill = 'totalAmountIhpApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountHaApproved, fill = 'totalAmountHaApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountOnaApproved, fill = 'totalAmountOnaApproved'), alpha = 0.5) +
  scale_fill_manual(values = c('totalNumberIaApproved' = '#1f77b4',  
                               'totalAmountIhpApproved' = '#2ca02c', 
                               'totalAmountHaApproved' = '#ff7f0e',  
                               'totalAmountOnaApproved' = '#d62728'), 
                    labels = c('totalNumberIaApproved' = 'Total Number IA Approved',
                               'totalAmountIhpApproved' = 'Total Amount IHP Approved',
                               'totalAmountHaApproved' = 'Total Amount HA Approved',
                               'totalAmountOnaApproved' = 'Total Amount ONA Approved')) +
  labs(x = "HOUSE UNIT", y = "Total Amount Approved", fill = "Metric" ,title = "state HOUSE UNIT with Total Amount Approved") +
  theme_classic()
```

### state poverty population with Total Amount Approved

```{r}
ggplot(amount_data, aes(x = Sum_Population_poverty_status_determined)) +
  geom_area(aes(y = totalNumberIaApproved, fill = 'totalNumberIaApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountIhpApproved, fill = 'totalAmountIhpApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountHaApproved, fill = 'totalAmountHaApproved'), alpha = 0.5) +
  geom_area(aes(y = totalAmountOnaApproved, fill = 'totalAmountOnaApproved'), alpha = 0.5) +
  scale_fill_manual(values = c('totalNumberIaApproved' = '#1f77b4',  
                               'totalAmountIhpApproved' = '#2ca02c', 
                               'totalAmountHaApproved' = '#ff7f0e',  
                               'totalAmountOnaApproved' = '#d62728'), 
                    labels = c('totalNumberIaApproved' = 'Total Number IA Approved',
                               'totalAmountIhpApproved' = 'Total Amount IHP Approved',
                               'totalAmountHaApproved' = 'Total Amount HA Approved',
                               'totalAmountOnaApproved' = 'Total Amount ONA Approved')) +
  labs(x = "poverty population", y = "Total Amount Approved", fill = "Metric" ,title = "state poverty population with Total Amount Approved") +
  theme_classic()
```

The above three figures all illustrate that the value of The total amount approved will increase with the increase of population, the number of house units and the poverty population. 

### the value of different types of public assistance grant funds available with different population, house unit, poverty population

```{r,message=F}
fund_data <- data_withflood |>
  filter(!(totalObligatedAmountCatAb == 0 & 
           totalObligatedAmountCatC2g == 0))|>
  pivot_longer(
    cols = c(Sum_Total_population, Sum_HOUSE_UNIT, Sum_Population_poverty_status_determined),
    names_to = "TotalType",
    values_to = "TypeValue"
  ) |>
  select(
    TotalType,
    TypeValue,
    totalObligatedAmountCatAb,
    totalObligatedAmountCatC2g
  ) |>
  pivot_longer(
    cols = starts_with("totalObligatedAmount"),
    names_to = "ObligationType",
    values_to = "Amount"
  )

ggplot(fund_data, aes(x = TypeValue, y = Amount, fill = ObligationType)) +
  geom_area(position = 'stack', alpha = 0.5) +
  facet_wrap(~TotalType, scales = 'free_x', ncol = 1) +
  scale_fill_brewer(palette = "Set1", name = "Obligation Type") +
  labs(
    x = "Value",
    y = "Total Obligated Amount ($)",
    title = "The Value of Different Types of Public Assistance Grant Funds\nAvailable with Different Population, House Unit, Poverty Population"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

The above three figures all illustrate that the value of The Public Assistance grant funding will increase with the increase in population, the number of house units, and the number of poor people.
